---
title: "Social Interactions at a Public High School"
author: "Lauren Treiman"
date: "8/3/2018"
output: html_document
---

This analysis was used to help an epidimeoly research project at the University of Utah investigate how interactions spread viruses such as the flu. This file contains the social network analysis for one high school in Salt Lake City. To obtain the data, students wore sensors that recorded how long and who a student interacted with. Students wore these sensors for two whole school days. 

For this project, I used R-markdown to create the html document and used packages such as igraph, dplyr, chron, and lubridate. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(igraph)
library(dplyr)
library(chron)
library(lubridate)
```

```{r}
# Download dsn
node <- read.csv("/Users/Laurenst1006/Desktop/U of U Research/Summer 2018/West/Nodeinfo WestDay1.csv")

nodeInfo <- read.csv("/Users/Laurenst1006/Desktop/U of U Research/Summer 2018/West/Nodeinfo WestDay2.csv")

schedule <- read.csv("/Users/Laurenst1006/Desktop/U of U Research/Summer 2018/West/West Schedule.csv")

dsn <- read.csv("/Users/Laurenst1006/Desktop/U of U Research/Summer 2018/West/West.csv")
```

```{r}
# Split data set into two times
dsn$west_days<- as.POSIXct(dsn$BeginDateTime) # Day 1
west_day1 <- dsn[day(dsn$west_days) == 20,] # Day 1
west_day2 <- dsn[day(dsn$west_days) == 21,] # Day 2

# For day 1, only use id/ contact if found in node file
ds1<-west_day1[west_day1[,"P1"]%in%node[,"SensorID1"]&west_day1[,"P2"]%in%node[,"SensorID1"],]

# Create variable ids that only displays ids and contacts in dsn frams
ids<-sort(unique(c(ds1[,"P1"],ds1[,"P2"])))

# Remove Duplicates in node file
node2 <- node[!duplicated(node$SensorID1),]

# Create dsn frame with ids only found in ids (to delete any extra)
node3<-node2[node2[,"SensorID1"]%in%ids,]

# Change ids to seq 1 -> length(ids)
node3[,"sensors"]<-0
ds1[,"id"]<-0
ds1[,"contact"]<-0
for(i in 1:length(ids)){
  node3[node3[,"SensorID1"]==ids[i],"sensors"]<-i
  ds1[ds1[,"P1"]==ids[i],"id"]<-i
  ds1[ds1[,"P2"]==ids[i],"contact"]<-i  
}

nodeFinal <- node3[,c("sensors", "GradeCat", "GenderCat", "Lunch")]
dsFinal <- ds1[,c("id", "contact", "TotalSeconds", "BeginDateTime", "EndDateTime", "Duration")]

# For day 2
ds2<-west_day2[west_day2[,"P1"]%in%nodeInfo[,"SensorID2"]&west_day2[,"P2"]%in%nodeInfo[,"SensorID2"],]

# Create variable ids that only displays ids and contacts in dsn frams
ids<-sort(unique(c(ds2[,"P1"],ds2[,"P2"])))

# Remove Duplicates in node file
nodeInfo2 <- nodeInfo[!duplicated(nodeInfo$SensorID2),]

# Create dsn frame with ids only found in ids (to delete any extra)
nodeInfo3<-nodeInfo2[nodeInfo2[,"SensorID2"]%in%ids,]

# Change ids to seq 1 -> length(ids)
nodeInfo3[,"sensors"]<-0
ds2[,"id"]<-0
ds2[,"contact"]<-0
for(i in 1:length(ids)){
  nodeInfo3[nodeInfo3[,"SensorID2"]==ids[i],"sensors"]<-i
  ds2[ds2[,"P1"]==ids[i],"id"]<-i
  ds2[ds2[,"P2"]==ids[i],"contact"]<-i  
}

nodeFinal2 <- nodeInfo3[,c("sensors", "GradeCat", "GenderCat", "Lunch")]
dsFinal2 <- ds2[,c("id", "contact", "TotalSeconds", "BeginDateTime", "EndDateTime", "Duration")]
```

```{r}
# Create period attribute
# Create time variable for schedule
tmp<- format(as.POSIXct(strptime(schedule$SegmentDateTime, "%Y-%m-%d %H:%M:%S", tz = "")), format = "%H:%M:%S")
sched <- tmp[1:11]

# Split time from date/time
# Day 1
time1<- format(as.POSIXct(strptime(dsFinal$BeginDateTime, "%Y-%m-%d %H:%M:%S", tz = "")), format = "%H:%M:%S")
# Day 2
time2<- format(as.POSIXct(strptime(dsFinal2$BeginDateTime, "%Y-%m-%d %H:%M:%S", tz = "")), format = "%H:%M:%S")

# Create period attribute for day 1
dsFinal[,"period"] <- "Before School"
dsFinal[time1 >= sched[2], "period"] <- "Period1"
dsFinal[time1 >= sched[3], "period"] <- "Hallway1"
dsFinal[time1 >= sched[4], "period"] <- "Period2"
dsFinal[time1 >= sched[5], "period"] <- "Hallway2"
# For Lunch 1 Students
# id = lunch 1, contact = lunch 1. period = lunch 1 (Interaction during lunchtime)
dsFinal[(time1 >= sched[6] & time1 < sched[7] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"]),"period"]<-"Lunch" 
# id = lunch 1, contact = lunch 2. period = lunch 1 (Interaction during lunchtime)
dsFinal[(time1 >= sched[6] & time1 < sched[7] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"]),"period"]<-"Lunch" 
# id = lunch 2, contact = lunch 1. period = lunch 1 (Interaction during lunchtime)
dsFinal[(time1 >= sched[6] & time1 < sched[7] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"]),"period"]<-"Lunch" 
# id = lunch 1, contact = lunch 1. period = period 3 (Interaction during period)
dsFinal[(time1 >= sched[7] & time1 < sched[9] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"]),"period"]<-"Period3" 
# For Lunch 2 Students
# id = lunch 2, contact = lunch 2. period = lunch 2 (Interaction during period3)
dsFinal[(time1 >= sched[6] & time1 < sched[8] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"]),"period"]<-"Period3" 
# id = lunch 2, contact = lunch 2. period = lunch 2 (Interaction during lunchtime)
dsFinal[(time1 >= sched[8] & time1 < sched[9] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"]),"period"]<-"Lunch" 
# id = lunch 1, contact = lunch 2. period = lunch 2 (Interaction during lunchtime)
dsFinal[(time1 >= sched[8] & time1 < sched[9] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"]),"period"]<-"Lunch" 
# id = lunch 2, contact = lunch 1. period = lunch 2 (Interaction during lunchtime)
dsFinal[(time1 >= sched[8] & time1 < sched[9] & dsFinal[,"id"]%in% nodeFinal[nodeFinal[,"Lunch"] =="2","sensors"] & dsFinal[,"contact"]%in% nodeFinal[nodeFinal[,"Lunch"] =="1","sensors"]),"period"]<-"Lunch" 
dsFinal[time1 >= sched[9], "period"] <- "Hallway3"
dsFinal[time1 >= sched[10], "period"] <- "Period4"
dsFinal[time1 >= sched[11], "period"] <- "After School"

# Create period attribute for day 2
dsFinal2[,"period"] <- "Before School"
dsFinal2[time2 >= sched[2], "period"] <- "Period1"
dsFinal2[time2 >= sched[3], "period"] <- "Hallway1"
dsFinal2[time2 >= sched[4], "period"] <- "Period2"
dsFinal2[time2 >= sched[5], "period"] <- "Hallway2"
# For Lunch 1 Students
# id = lunch 1, contact = lunch 1. period = lunch 1 (Interaction during lunchtime)
dsFinal2[(time2 >= sched[6] & time2 < sched[7] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"]),"period"]<-"Lunch" 
# id = lunch 1, contact = lunch 2. period = lunch 1 (Interaction during lunchtime)
dsFinal2[(time2 >= sched[6] & time2 < sched[7] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"]),"period"]<-"Lunch" 
# id = lunch 2, contact = lunch 1. period = lunch 1 (Interaction during lunchtime)
dsFinal2[(time2 >= sched[6] & time2 < sched[7] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"]),"period"]<-"Lunch" 
# id = lunch 1, contact = lunch 1. period = period 3 (Interaction during period)
dsFinal2[(time2 >= sched[7] & time2 < sched[9] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"]),"period"]<-"Period3" 
# For Lunch 2 Students
# id = lunch 2, contact = lunch 2. period = lunch 2 (Interaction during period3)
dsFinal2[(time2 >= sched[6] & time2 < sched[8] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"]),"period"]<-"Period3" 
# id = lunch 2, contact = lunch 2. period = lunch 2 (Interaction during lunchtime)
dsFinal2[(time2 >= sched[8] & time2 < sched[9] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"]),"period"]<-"Lunch" 
# id = lunch 1, contact = lunch 2. period = lunch 2 (Interaction during lunchtime)
dsFinal2[(time2 >= sched[8] & time2 < sched[9] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"]),"period"]<-"Lunch" 
# id = lunch 2, contact = lunch 1. period = lunch 2 (Interaction during lunchtime)
dsFinal2[(time2 >= sched[8] & time2 < sched[9] & dsFinal2[,"id"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="2","sensors"] & dsFinal2[,"contact"]%in% nodeFinal2[nodeFinal2[,"Lunch"] =="1","sensors"]),"period"]<-"Lunch" 
dsFinal2[time2 >= sched[9], "period"] <- "Hallway3"
dsFinal2[time2 >= sched[10], "period"] <- "Period4"
dsFinal2[time2 >= sched[11], "period"] <- "After School"
```

```{r}
# Names
names_plot <- c("P1", "H1", "P2", "H2", "L", "P3", "H3", "P4")
names_order <- c("AS", "H1", "H2", "H3", "L", "P1", "P2", "P3", "P4")
names <- c("All day", "All periods", "Period 1", "Hallway 1", "Period 2", "Hallway 2", "Lunch", "Period 3", "Hallway 3", "Period 4")
```

#Summary of Network 

There are two networks for each day of the experiment. There are 4 90 minute periods, 3 6 minute hallway passings, and 2 30 minute lunches. 

Day 1

```{r}
west <- graph.data.frame(dsFinal, directed = F, vertices = nodeFinal)
summary(west)
```
```{r}
# Create lunch network 
westLunch<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Lunch"])

# west Period
tmp <-delete.edges(west,E(west)[get.edge.attribute(west,name="period")=="Lunch"]) 
tmp2 <-delete.edges(tmp, E(tmp)[get.edge.attribute(tmp,name="period")=="Hallway1"]) 
tmp3 <- delete.edges(tmp2, E(tmp2)[get.edge.attribute(tmp2,name="period")=="Hallway2"])
tmp4 <- delete.edges(tmp3, E(tmp3)[get.edge.attribute(tmp3,name="period")=="After School"])
westPeriod <- delete.edges(tmp4,E(tmp4)[get.edge.attribute(tmp4,name="period")=="Hallway3"])

# West Periods 1 - 4
westPeriod1<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Period1"])
westPeriod2<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Period2"])
westPeriod3<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Period3"])
westPeriod4<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Period4"])

# West Hallway 1 -3
westHallway1<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Hallway1"])

westHallway2<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Hallway2"])

westHallway3<-delete.edges(west,E(west)[get.edge.attribute(west,name="period")!="Hallway3"])
```

For day 1, there were 1425 students who participated and 153999 interactions. 
Day 2

```{r}
west2 <- graph.data.frame(dsFinal2, directed = F, vertices = nodeFinal2)
summary(west2)
```
```{r}
# Create lunch network 
west2Lunch<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Lunch"])

# west2 Period
tmp <-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")=="Lunch"]) 
tmp2 <-delete.edges(tmp, E(tmp)[get.edge.attribute(tmp,name="period")=="Hallway1"]) 
tmp3 <- delete.edges(tmp2, E(tmp2)[get.edge.attribute(tmp2,name="period")=="Hallway2"])
tmp4 <- delete.edges(tmp3, E(tmp3)[get.edge.attribute(tmp3,name="period")=="After School"])
west2Period <- delete.edges(tmp4,E(tmp4)[get.edge.attribute(tmp4,name="period")=="Hallway3"])

# west2 Periods 1 - 4
west2Period1<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Period1"])
west2Period2<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Period2"])
west2Period3<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Period3"])
west2Period4<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Period4"])

# west2 Hallway 1 -3
west2Hallway1<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Hallway1"])

west2Hallway2<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Hallway2"])

west2Hallway3<-delete.edges(west2,E(west2)[get.edge.attribute(west2,name="period")!="Hallway3"])
```

For day 2, there were 1220 students who participated and 556935 interavtions. 

# Distribution 

I graphed the distribution of the number of interactions for each hallway, period and lunches, and after school. Both lunches are grouped together. Also, it is important to note that sensors were handed out to students in period 1, so there is an overestimate of total interactions for period 1. 

Day 1 

```{r}
dist1 <- ftable(E(west)$period)
dist1 
dist1 <- barplot(dist1, main = "Distribution of contacts (Day 1)", xlab = "Period", ylab = "Frequency", names.arg = names_order)
```
(AS = After School)

Day 2

```{r}
dist2 <- ftable(E(west2)$period)
dist2 
dist2 <- barplot(dist2, main = "Distribution of contacts (Day 2)", xlab = "Period", ylab = "Frequency", names.arg = names_order)
```

#Interactions Throughout the Day

The two plots show the new interactions as the day progresses. 
Day 1

```{r}
# Calculate new Interactions Throughout the Day
time<- format(as.POSIXct(strptime(E(west)$BeginDateTime, "%Y-%m-%d %H:%M:%S", tz = "")), format = "%H:%M:%S")
# Convert Times into numerical integers
timeNum <- as.numeric(chron(times.= time))
# Create edge attribute
E(west)$time <- timeNum

TS1 <- seq(from = .350, to = .60, by = .01)
NewContacts1 <- numeric()
for (i in TS1){
  tmp1 <- delete.edges(west, E(west)[get.edge.attribute(west,name="time") > i]) 
  tmpEL1 <- as.data.frame(get.edgelist(tmp1))
  tmpEL1 <- tmpEL1%>%
    distinct(.keep_all = TRUE)
  NewContacts1 <- c(NewContacts1, nrow(tmpEL1))
}
NewContacts1 <- data.frame(Times = TS1, NewContacts = NewContacts1, stringsAsFactors = FALSE)

plot(NewContacts1, type = 'l', main = "New Contacts (Day 1)")
```

```{r}
# Calculate new Interactions Throughout the Day
time2<- format(as.POSIXct(strptime(E(west2)$BeginDateTime, "%Y-%m-%d %H:%M:%S", tz = "")), format = "%H:%M:%S")
# Convert Times into numerical integers
time2Num <- as.numeric(chron(times.= time2))
# Create edge attribute
E(west2)$time <- time2Num

TS2 <- seq(from = .350, to = .60, by = .01)
NewContacts2 <- numeric()
for (i in TS2){
  tmp2 <- delete.edges(west2, E(west2)[get.edge.attribute(west2,name="time") > i]) 
  tmpEL2 <- as.data.frame(get.edgelist(tmp2))
  tmpEL2 <- tmpEL2%>%
    distinct(.keep_all = TRUE)
  NewContacts2 <- c(NewContacts2, nrow(tmpEL2))
}
NewContacts2 <- data.frame(Times = TS2, NewContacts = NewContacts2, stringsAsFactors = FALSE)

plot(NewContacts2, type = 'l', main = "New Contacts (Day 2)")
```


I then looked at different social networking attributes including degree, betweenness, closeness, transitivity, density and assortativity. 

# Degree


Day 1 

```{r}
deg_day1 <- data.frame(matrix(0, ncol = 7, nrow = 10))
names(deg_day1) <- c("Measure", "Min", "Q1", 'Median', 'Mean', 'Q3', 'Max')
deg_day1[,1]<-names
deg_day1[1,2:7] <- summary(degree(west))
deg_day1[2,2:7] <- summary(degree(westPeriod))
deg_day1[3,2:7] <- summary(degree(westPeriod1))
deg_day1[5,2:7] <- summary(degree(westPeriod2))
deg_day1[8,2:7] <- summary(degree(westPeriod3))
deg_day1[10,2:7] <- summary(degree(westPeriod4))
deg_day1[7, 2:7] <- summary(degree(westLunch))
deg_day1[4,2:7] <- summary(degree(westHallway1))
deg_day1[6,2:7] <- summary(degree(westHallway2))
deg_day1[9,2:7] <- summary(degree(westHallway3))
deg_day1

deg_day1Plot <- deg_day1[3:10,5]
plot(deg_day1Plot, type = 'l', col = "red", xaxt = 'n', main = "Degree (Mean) (Day 1)", xlab = "Time of Day", ylab = "Degree")
axis(1, at = 1:8, labels = names_plot)
```

Day 2 

```{r}
deg_day2 <- data.frame(matrix(0, ncol = 7, nrow = 10))
names(deg_day2) <- c("Measure", "Min", "Q1", 'Median', 'Mean', 'Q3', 'Max')
deg_day2[,1]<-names
deg_day2[1,2:7] <- summary(degree(west2))
deg_day2[2,2:7] <- summary(degree(west2Period))
deg_day2[3,2:7] <- summary(degree(west2Period1))
deg_day2[5,2:7] <- summary(degree(west2Period2))
deg_day2[8,2:7] <- summary(degree(west2Period3))
deg_day2[10,2:7] <- summary(degree(west2Period4))
deg_day2[7, 2:7] <- summary(degree(west2Lunch))
deg_day2[4,2:7] <- summary(degree(west2Hallway1))
deg_day2[6,2:7] <- summary(degree(west2Hallway2))
deg_day2[9,2:7] <- summary(degree(west2Hallway3))
deg_day2

# Plot 
deg_day2Plot <- deg_day2[3:10,5]
plot(deg_day2Plot, type = 'l', col = "blue", xaxt = 'n', main = "Degree (Mean) (Day 2)", xlab = "Time of Day", ylab = "Degree")
axis(1, at = 1:8, labels = names_plot)
```

```{r}
# Comparison between days
plot(deg_day1Plot, type = 'l', col = "red", xaxt = 'n', main = "Comparison of degree for each day", xlab = "Time of Day", ylab = "Degree", ylim = c(0,800))
axis(1, at = 1:8, labels = names_plot)
lines(deg_day2Plot, col = "blue", type = "l")
legend("top", fill = c("red", "blue"), legend = c("Day1", "Day2"), horiz = T, cex = 0.7)
```

# Betweenness 

Day 1 

```{r}
bet_day1 <- data.frame(matrix(0, ncol = 7, nrow = 10))
names(bet_day1) <- c("Measure", "Min", "Q1", 'Median', 'Mean', 'Q3', 'Max')
bet_day1[,1]<-names
bet_day1[1,2:7] <- summary(betweenness(west))
bet_day1[2,2:7] <- summary(betweenness(westPeriod))
bet_day1[3,2:7] <- summary(betweenness(westPeriod1))
bet_day1[5,2:7] <- summary(betweenness(westPeriod2))
bet_day1[8,2:7] <- summary(betweenness(westPeriod3))
bet_day1[10,2:7] <- summary(betweenness(westPeriod4))
bet_day1[7, 2:7] <- summary(betweenness(westLunch))
bet_day1[4,2:7] <- summary(betweenness(westHallway1))
bet_day1[6,2:7] <- summary(betweenness(westHallway2))
bet_day1[9,2:7] <- summary(betweenness(westHallway3))
bet_day1

# Plot
bet_day1Plot <- bet_day1[3:10,4]
plot(bet_day1Plot, type = 'l', col = "red", xaxt = 'n', main = "Betweenness (Median) (Day 1)", xlab = "Time of Day", ylab = "Betweenness")
axis(1, at = 1:8, labels = names_plot)
```

Day 2 

```{r}
bet_day2 <- data.frame(matrix(0, ncol = 7, nrow = 10))
names(bet_day2) <- c("Measure", "Min", "Q1", 'Median', 'Mean', 'Q3', 'Max')
bet_day2[,1]<-names
bet_day2[1,2:7] <- summary(betweenness(west2))
bet_day2[2,2:7] <- summary(betweenness(west2Period))
bet_day2[3,2:7] <- summary(betweenness(west2Period1))
bet_day2[5,2:7] <- summary(betweenness(west2Period2))
bet_day2[8,2:7] <- summary(betweenness(west2Period3))
bet_day2[10,2:7] <- summary(betweenness(west2Period4))
bet_day2[7, 2:7] <- summary(betweenness(west2Lunch))
bet_day2[4,2:7] <- summary(betweenness(west2Hallway1))
bet_day2[6,2:7] <- summary(betweenness(west2Hallway2))
bet_day2[9,2:7] <- summary(betweenness(west2Hallway3))
bet_day2

# Plot 
bet_day2Plot <- bet_day2[3:10,4]
plot(bet_day2Plot, type = 'l', col = "blue", xaxt = 'n', main = "Betweenness (Median) (Day 2)", xlab = "Time of Day", ylab = "betweenness")
axis(1, at = 1:8, labels = names_plot)
```

```{r}
# Comparison between days
bet_day1Plot <- bet_day1[3:10,4]
plot(bet_day1Plot, type = 'l', col = "red", xaxt = 'n', main = "Comparison of betweenness for each day", xlab = "Time of Day", ylab = "Betweenness")
axis(1, at = 1:8, labels = names_plot)
lines(bet_day2Plot, col = "blue", type = "l")
legend("topright", fill = c("red", "blue"), legend = c("Day1", "Day2"), horiz = T, cex = 0.7)
```


# Closeness

Day 1 

```{r}
clo_day1 <- data.frame(matrix(0, ncol = 7, nrow = 10))
names(clo_day1) <- c("Measure", "Min", "Q1", 'Median', 'Mean', 'Q3', 'Max')
clo_day1[,1]<-names
clo_day1[1,2:7] <- summary(closeness(west))
clo_day1[2,2:7] <- summary(closeness(westPeriod))
clo_day1[3,2:7] <- summary(closeness(westPeriod1))
clo_day1[5,2:7] <- summary(closeness(westPeriod2))
clo_day1[8,2:7] <- summary(closeness(westPeriod3))
clo_day1[10,2:7] <- summary(closeness(westPeriod4))
clo_day1[7, 2:7] <- summary(closeness(westLunch))
clo_day1[4,2:7] <- summary(closeness(westHallway1))
clo_day1[6,2:7] <- summary(closeness(westHallway2))
clo_day1[9,2:7] <- summary(closeness(westHallway3))
clo_day1

clo_day1Plot <- clo_day1[3:10,4]
plot(clo_day1Plot, type = 'l', col = "red", xaxt = 'n', main = "closeness (Median) (Day 1)", xlab = "Time of Day", ylab = "closeness")
axis(1, at = 1:8, labels = names_plot)
```

Day 2 

```{r}
clo_day2 <- data.frame(matrix(0, ncol = 7, nrow = 10))
names(clo_day2) <- c("Measure", "Min", "Q1", 'Median', 'Mean', 'Q3', 'Max')
clo_day2[,1]<-names
clo_day2[1,2:7] <- summary(closeness(west2))
clo_day2[2,2:7] <- summary(closeness(west2Period))
clo_day2[3,2:7] <- summary(closeness(west2Period1))
clo_day2[5,2:7] <- summary(closeness(west2Period2))
clo_day2[8,2:7] <- summary(closeness(west2Period3))
clo_day2[10,2:7] <- summary(closeness(west2Period4))
clo_day2[7, 2:7] <- summary(closeness(west2Lunch))
clo_day2[4,2:7] <- summary(closeness(west2Hallway1))
clo_day2[6,2:7] <- summary(closeness(west2Hallway2))
clo_day2[9,2:7] <- summary(closeness(west2Hallway3))
clo_day2

# Plot 
clo_day2Plot <- clo_day2[3:10,4]
plot(clo_day2Plot, type = 'l', col = "blue", xaxt = 'n', main = "closeness (Median) (Day 2)", xlab = "Time of Day", ylab = "closeness")
axis(1, at = 1:8, labels = names_plot)
```

```{r}
# Comparison between days
plot(clo_day1Plot, type = 'l', col = "red", xaxt = 'n', main = "Comparison of closeness for each day", xlab = "Time of Day", ylab = "Closeness", ylim = c(2e-6, 1.6e-5))
axis(1, at = 1:8, labels = names_plot)
lines(clo_day2Plot, col = "blue", type = "l")
legend("topleft", fill = c("red", "blue"), legend = c("Day1", "Day2"), horiz = T, cex = 0.7)
```

# Transitivity

```{r}
trans <- data.frame(matrix(0, nrow = 10, ncol = 3))
names(trans)<- c("Measure", "Day1","Day2")
trans[,1]<- names

# Day 1
trans[1,2] <- transitivity(west)
trans[2,2] <- transitivity(westPeriod)
trans[3,2] <- transitivity(westPeriod1)
trans[5,2] <- transitivity(westPeriod2)
trans[8,2] <- transitivity(westPeriod3)
trans[10,2] <- transitivity(westPeriod4)
trans[4,2] <- transitivity(westHallway1)
trans[6,2] <- transitivity(westHallway2)
trans[9,2] <- transitivity(westHallway3)
trans[7,2] <- transitivity(westLunch)

# Day 2
trans[1,3] <- transitivity(west2)
trans[2,3] <- transitivity(west2Period)
trans[3,3] <- transitivity(west2Period1)
trans[5,3] <- transitivity(west2Period2)
trans[8,3] <- transitivity(west2Period3)
trans[10,3] <- transitivity(west2Period4)
trans[4,3] <- transitivity(west2Hallway1)
trans[6,3] <- transitivity(west2Hallway2)
trans[9,3] <- transitivity(west2Hallway3)
trans[7,3] <- transitivity(west2Lunch)

trans
```

```{r}
# Plot transitivity
trans_1Plot <- trans[3:10,2]
trans_2Plot <- trans[3:10,3]
plot(trans_1Plot, type = 'l', col = "red", ylab = "Transitivity", xlab = "Time of Day", main = "Transitivity", xaxt = 'n', ylim = c(0.05, 1))
lines(trans_2Plot, col = "blue")
axis(1, at = 1:8, names_plot)
legend("top", fill = c("red", "blue"), legend = c("Day1", "Day2"), horiz = T, cex = 0.7)
```

# Density

```{r}
dense <- data.frame(matrix(0, nrow = 10, ncol = 3))
names(dense) <- c("Measure", "Day1", "Day2")
dense[,1] <- names

# Day1
dense[1,2] <- edge_density(west)
dense[2,2] <- edge_density(westPeriod)
dense[3,2] <- edge_density(westPeriod1)
dense[5,2] <- edge_density(westPeriod2)
dense[8,2] <- edge_density(westPeriod3)
dense[10,2] <- edge_density(westPeriod4)
dense[4,2] <- edge_density(westHallway1)
dense[6,2] <- edge_density(westHallway2)
dense[9,2] <- edge_density(westHallway3)
dense[7,2] <- edge_density(westLunch)

# Day2
dense[1,3] <- edge_density(west2)
dense[2,3] <- edge_density(west2Period)
dense[3,3] <- edge_density(west2Period1)
dense[5,3] <- edge_density(west2Period2)
dense[8,3] <- edge_density(west2Period3)
dense[10,3] <- edge_density(west2Period4)
dense[4,3] <- edge_density(west2Hallway1)
dense[6,3] <- edge_density(west2Hallway2)
dense[9,3] <- edge_density(west2Hallway3)
dense[7,3] <- edge_density(west2Lunch)

dense
```

```{r}
# Plot density
dense_1Plot <- dense[3:10, 2]
dense_2Plot <- dense[3:10, 3]

plot(dense_1Plot, type = 'l', col = "red", xlab = "Time of Day", ylab = "Density", main = "Density", xaxt = 'n', ylim = c(0,.65))
lines(dense_2Plot, col = "blue")
axis(1, at = 1:8, labels = names_plot)
legend("top", fill = c("red", "blue"), legend = c("Day1", "Day2"), horiz = T, cex = 0.7)
```

# Assortativity

I looked at 4 different reasons why a student would be more likely to interact with another student: if they were the same gender, in the same grade, had the same lunch, or interacted with the same number of students. 

Day 1

```{r}
assor_1 <- data.frame(matrix(0, nrow = 10, ncol = 5))
names(assor_1) <- c("Measure", "Degree", "GenderCat", "GradeCat", "Lunch")
assor_1[,1] <- names

# Degree
assor_1[1,2] <- assortativity_degree(west)
assor_1[2,2] <- assortativity_degree(westPeriod)
assor_1[3,2] <- assortativity_degree(westPeriod1)
assor_1[4,2] <- assortativity_degree(westHallway1)
assor_1[5,2] <- assortativity_degree(westPeriod2)
assor_1[6,2] <- assortativity_degree(westHallway2)
assor_1[7,2] <- assortativity_degree(westLunch)
assor_1[8,2] <- assortativity_degree(westPeriod3)
assor_1[9,2] <- assortativity_degree(westHallway3)
assor_1[10,2] <- assortativity_degree(westPeriod4)

# GenderCat
assor_1[1,3] <-assortativity(west, V(west)$GenderCat)
assor_1[2,3] <-assortativity(westPeriod, V(westPeriod)$GenderCat)
assor_1[3,3] <-assortativity(westPeriod1, V(westPeriod1)$GenderCat)
assor_1[4,3] <-assortativity(westHallway1, V(westHallway1)$GenderCat)
assor_1[5,3] <-assortativity(westPeriod2, V(westPeriod2)$GenderCat)
assor_1[6,3] <-assortativity(westHallway2, V(westHallway2)$GenderCat)
assor_1[7,3] <-assortativity(westLunch, V(westLunch)$GenderCat)
assor_1[8,3] <-assortativity(westPeriod3, V(westPeriod3)$GenderCat)
assor_1[9,3] <-assortativity(westHallway3, V(westHallway3)$GenderCat)
assor_1[10,3] <-assortativity(westPeriod4, V(westPeriod4)$GenderCat)

# GradeCat
assor_1[1,4] <-assortativity(west, V(west)$GradeCat)
assor_1[2,4] <-assortativity(westPeriod, V(westPeriod)$GradeCat)
assor_1[3,4] <-assortativity(westPeriod1, V(westPeriod1)$GradeCat)
assor_1[4,4] <-assortativity(westHallway1, V(westHallway1)$GradeCat)
assor_1[5,4] <-assortativity(westPeriod2, V(westPeriod2)$GradeCat)
assor_1[6,4] <-assortativity(westHallway2, V(westHallway2)$GradeCat)
assor_1[7,4] <-assortativity(westLunch, V(westLunch)$GradeCat)
assor_1[8,4] <-assortativity(westPeriod3, V(westPeriod3)$GradeCat)
assor_1[9,4] <-assortativity(westHallway3, V(westHallway3)$GradeCat)
assor_1[10,4] <-assortativity(westPeriod4, V(westPeriod4)$GradeCat)

# Lunch
assor_1[1,5] <-assortativity(west, V(west)$Lunch)
assor_1[2,5] <-assortativity(westPeriod, V(westPeriod)$Lunch)
assor_1[3,5] <-assortativity(westPeriod1, V(westPeriod1)$Lunch)
assor_1[4,5] <-assortativity(westHallway1, V(westHallway1)$Lunch)
assor_1[5,5] <-assortativity(westPeriod2, V(westPeriod2)$Lunch)
assor_1[6,5] <-assortativity(westHallway2, V(westHallway2)$Lunch)
assor_1[7,5] <-assortativity(westLunch, V(westLunch)$Lunch)
assor_1[8,5] <-assortativity(westPeriod3, V(westPeriod3)$Lunch)
assor_1[9,5] <-assortativity(westHallway3, V(westHallway3)$Lunch)
assor_1[10,5] <-assortativity(westPeriod4, V(westPeriod4)$Lunch)

assor_1
```

```{r}
# Plot 
assor_1Tot <- assor_1[3:10,2]
assor_1Gen <- assor_1[3:10,3]
assor_1Gra <- assor_1[3:10,4]
assor_1Lun <- assor_1[3:10,5]

plot(assor_1Tot, type = 'l', col = "green3", main = "Assortativity (Day1)", ylab = "Assortativity", xlab = "Time of Day", xaxt = 'n', ylim = c(0,1))
lines(assor_1Gen, col = "hotpink")
lines(assor_1Gra, col = "cyan")
lines(assor_1Lun, col = "darkviolet")
axis(1, at = 1:8, names_plot)
legend("top", legend = c("Degree", "Gender", "Grade", "Lunch"), fill = c("green3", "hotpink", "cyan", "darkviolet"), horiz = T, cex = 0.6)
```

Day 2

```{r}
assor_2 <- data.frame(matrix(0, nrow = 10, ncol = 5))
names(assor_2) <- c("Measure", "Degree", "GenderCat", "GradeCat", "Lunch")
assor_2[,1] <- names

# Degree
assor_2[1,2] <- assortativity_degree(west2)
assor_2[2,2] <- assortativity_degree(west2Period)
assor_2[3,2] <- assortativity_degree(west2Period1)
assor_2[4,2] <- assortativity_degree(west2Hallway1)
assor_2[5,2] <- assortativity_degree(west2Period2)
assor_2[6,2] <- assortativity_degree(west2Hallway2)
assor_2[7,2] <- assortativity_degree(west2Lunch)
assor_2[8,2] <- assortativity_degree(west2Period3)
assor_2[9,2] <- assortativity_degree(west2Hallway3)
assor_2[10,2] <- assortativity_degree(west2Period4)

# GenderCat
assor_2[1,3] <-assortativity(west2, V(west2)$GenderCat)
assor_2[2,3] <-assortativity(west2Period, V(west2Period)$GenderCat)
assor_2[3,3] <-assortativity(west2Period1, V(west2Period1)$GenderCat)
assor_2[4,3] <-assortativity(west2Hallway1, V(west2Hallway1)$GenderCat)
assor_2[5,3] <-assortativity(west2Period2, V(west2Period2)$GenderCat)
assor_2[6,3] <-assortativity(west2Hallway2, V(west2Hallway2)$GenderCat)
assor_2[7,3] <-assortativity(west2Lunch, V(west2Lunch)$GenderCat)
assor_2[8,3] <-assortativity(west2Period3, V(west2Period3)$GenderCat)
assor_2[9,3] <-assortativity(west2Hallway3, V(west2Hallway3)$GenderCat)
assor_2[10,3] <-assortativity(west2Period4, V(west2Period4)$GenderCat)

# GradeCat
assor_2[1,4] <-assortativity(west2, V(west2)$GradeCat)
assor_2[2,4] <-assortativity(west2Period, V(west2Period)$GradeCat)
assor_2[3,4] <-assortativity(west2Period1, V(west2Period1)$GradeCat)
assor_2[4,4] <-assortativity(west2Hallway1, V(west2Hallway1)$GradeCat)
assor_2[5,4] <-assortativity(west2Period2, V(west2Period2)$GradeCat)
assor_2[6,4] <-assortativity(west2Hallway2, V(west2Hallway2)$GradeCat)
assor_2[7,4] <-assortativity(west2Lunch, V(west2Lunch)$GradeCat)
assor_2[8,4] <-assortativity(west2Period3, V(west2Period3)$GradeCat)

# Lunch
assor_2[1,5] <-assortativity(west2, V(west2)$Lunch)
assor_2[2,5] <-assortativity(west2Period, V(west2Period)$Lunch)
assor_2[3,5] <-assortativity(west2Period1, V(west2Period1)$Lunch)
assor_2[4,5] <-assortativity(west2Hallway1, V(west2Hallway1)$Lunch)
assor_2[5,5] <-assortativity(west2Period2, V(west2Period2)$Lunch)
assor_2[6,5] <-assortativity(west2Hallway2, V(west2Hallway2)$Lunch)
assor_2[7,5] <-assortativity(west2Lunch, V(west2Lunch)$Lunch)
assor_2[8,5] <-assortativity(west2Period3, V(west2Period3)$Lunch)
assor_2[9,5] <-assortativity(west2Hallway3, V(west2Hallway3)$Lunch)
assor_2[10,5] <-assortativity(west2Period4, V(west2Period4)$Lunch)

assor_2
```

```{r}
# Plot 
assor_2Tot <- assor_2[3:10,2]
assor_2Gen <- assor_2[3:10,3]
assor_2Gra <- assor_2[3:10,4]
assor_2Lun <- assor_2[3:10,5]

plot(assor_2Tot, type = 'l', col = "green3", main = "Assortativity (Day2)", ylab = "Assortativity", xlab = "Time of Day", xaxt = 'n', ylim = c(-.2,1))
lines(assor_2Gen, col = "hotpink")
lines(assor_2Gra, col = "cyan")
lines(assor_2Lun, col = "darkviolet")
axis(1, at = 1:8, names_plot)
legend("top", legend = c("Degree", "Gender", "Grade", "Lunch"), fill = c("green3", "hotpink", "cyan", "darkviolet"), horiz = T, cex = 0.6)
```

Comparing each characteristic:

```{r}
# Total
plot(assor_1Tot, type = 'l', col = "red", ylab = "Assortativity", xlab = "Time of Day", main = "Assortativity (Degree)", xaxt = 'n', ylim = c(0,.7))
lines(assor_2Tot, col = "blue")
axis(1, at = 1:8, labels = names_plot)
legend("top", fill = c("red", "blue"), legend = c("Day 1", "Day 2"), horiz = T, cex = 0.6)
```

```{r}
# Gender
plot(assor_1Gen, type = 'l', col = "red", ylab = "Assortativity", xlab = "Time of Day", main = "Assortativity (Gender)", xaxt = 'n', ylim = c(-.2,.7))
lines(assor_2Gen, col = "blue")
axis(1, at = 1:8, labels = names_plot)
legend("top", fill = c("red", "blue"), legend = c("Day 1", "Day 2"), horiz = T, cex = 0.6)
```

```{r}
# Grade
plot(assor_1Gra, type = 'l', col = "red", ylab = "Assortativity", xlab = "Time of Day", main = "Assortativity (Grade)", xaxt = 'n', ylim = c(-.1,.9))
lines(assor_2Gra, col = "blue")
axis(1, at = 1:8, labels = names_plot)
legend("top", fill = c("red", "blue"), legend = c("Day 1", "Day 2"), horiz = T, cex = 0.6)
```

```{r}
# Lunch
plot(assor_1Lun, type = 'l', col = "red", ylab = "Assortativity", xlab = "Time of Day", main = "Assortativity (Lunch)", xaxt = 'n', ylim = c(0,1))
lines(assor_2Lun, col = "blue")
axis(1, at = 1:8, labels = names_plot)
legend("top", fill = c("red", "blue"), legend = c("Day 1", "Day 2"), horiz = T, cex = 0.6)
```


